Epidemic Tracking and Forecasting: Lessons Learned from a Tumultuous Year

### 2021-12-07 perspective/paper.tex
Typo in acks

This material is based on work supported by gifts from Google.or and the McCune 
Foundation; and by Centers for Disease Control and Prevention (CDC) grant
U01IP001121.

>>>>

This material is based on work supported by gifts from Google.org and the McCune  
Foundation; and by Centers for Disease Control and Prevention (CDC) grant
U01IP001121.
